Kids PM Summary

### 2020-07-22 manuscript_tables_figures.Rmd
summary stat and plot updates

>>>>

```{r, fig.height=1.25, fig.width=4.15}
# Poster figures

plot_data <- health_exposure_data_sampling_day %>% 
  mutate(income_3level = factor(income_3level, 
                                labels = c("< $20,000", "$20,000-$49,999", "$50,000+")),
         chimney_clean_3level = factor(chimney_clean_3level, 
                                labels = c("< 6 months ago", "6-12 months ago", "12 + months ago")),
         stove_grade_3level = factor(stove_grade_3level, 
                                labels = c("High-quality", "Medium-quality", "Low-quality")),
         area = factor(area,
                       labels = c("Alaska", "Navajo Nation", "Western Montana")))

home_char_function <- function(data, var, title_label) {

  home_char_plot <- data %>% 
  filter(winter_id == 1 & treatment_assigned == "Placebo") %>% 
  arrange(area, home, sampling_day) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  select(area, var) %>% 
  rename(plot_var = var) %>% 
  filter(!is.na(plot_var)) %>% 
  ggplot() +
    geom_bar(aes(fct_rev(plot_var), fill = area)) +
    theme_minimal() +
    coord_flip() +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          title = element_text(size = 16, colour = "black"),
          legend.text = element_blank(),
          legend.title = element_blank(),
          legend.position = "",
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    labs(title = title_label) +
    scale_fill_manual(values = cbPalette)
  home_char_plot

}

home_char_function(plot_data, "income_3level", "Household income")
home_char_function(plot_data, "residents_under5_2level", "Kids < 5 years of age")
home_char_function(plot_data, "home_floors_2level", "Home floors/levels")
home_char_function(plot_data, "stove_age_3level", "Stove age")
home_char_function(plot_data, "chimney_clean_3level", "Chimney cleaned")
home_char_function(plot_data, "wood_collect_2level", "Wood collected")
home_char_function(plot_data, "stove_grade_3level", "Stove grade")
```

### 2020-07-22 pm_summary.Rmd
summary stat and plot updates

```{r, fig.height=, fig.width=8}
boxplots_kids_pm <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1 & treatment_assigned == "Placebo") %>% 
  arrange(area, home, sampling_day) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  ggplot(aes(area, pm_mean_sampling_period)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red") +
    #scale_y_log10() +
    theme_minimal() +
    labs(y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black",
                                      margin = margin(t = 0, r = 0, b = 30, l = 0)),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_pm

ggsave("boxplots_kids_pm.jpg", height = 7, width = 8)
```

>>>>

```{r, fig.height=4, fig.width=3}
boxplots_kids_pm <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1 & treatment_assigned == "Placebo") %>% 
  arrange(area, home, sampling_day) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  ggplot(aes(area, pm_mean_sampling_period)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    stat_summary(fun.y=mean, geom="point", shape=17, size=4, color="red") +
    #scale_y_log10() +
    theme_minimal() +
    labs(y = expression(paste("PM"[2.5], " (", mu, g/m^3, ")"))) +
    theme(axis.text.x = element_text(size = 16, colour = "black",
                                      margin = margin(t = 0, r = 0, b = 30, l = 0)),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank())
boxplots_kids_pm

ggsave("boxplots_kids_pm.jpg", height = 7, width = 4)
```
